Attributes-based Object Classification and Segmentation

### 2010-05-12 trunk/paper.tex
paper looks good

\begin{table}
\centering
\begin{tabular}{|l|l|l|}
\hline Methods & Precision(\%) & Recall(\%) \\
\hline LowFea  & 55.97 & 70.96 \\
\hline Att1    & 51.89 & 51.89 \\
\hline Random  & 35.19 & 50.00 \\
\hline Add     & 60.82 & 54.06 \\
\hline
\end{tabular}
\caption{Object classification results of three baseline methods and the proposed additive algorithm.}
\label{table:aresults}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/add_res/roc_class.png.eps}
\caption{Result of adjusting the factor $f$ in the subtractive
algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
that \subref{fig:fb} retains more of the cars, especially the two
closest on the right and left, but also has more false-positive
pixels, such as the ceiling region of the parking garage.}
\label{fig:roc_class}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/add_res/roc_seg.png.eps}
\caption{Result of adjusting the factor $f$ in the subtractive
algorithm. \subref{fig:fa} shows running the algorithm with $f=0.9$
and \subref{fig:fb} shows running the algorithm with $f=1.0$.  Note
that \subref{fig:fb} retains more of the cars, especially the two
closest on the right and left, but also has more false-positive
pixels, such as the ceiling region of the parking garage.}
\label{fig:roc_seg}
\end{figure}

@@

\includegraphics[width=2.95cm]{figures/sub_results/2008_007064_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_000052_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_007171_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_000251_1_bad_sub.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f$ at different values
between 0.9 and 1.0.}
\label{fig:car_good_results}
\end{figure*}

@@

\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f$ at different values
between 0.9 and 1.0.}
\label{fig:car_bad_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg_2_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of planes from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.}
\label{fig:aeroplane_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg_2_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg_2_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg_2_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg_2_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of planes from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.}
\label{fig:aeroplane_bad_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg_3_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of horses from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.}
\label{fig:horse_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg_3_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg_3_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg_3_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg_3_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of horses from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.}
\label{fig:horse_bad_results}
\end{figure*}

@@

As object classification is generally only as good as the features used, so also it
appears that this approach to segmentation is only as good as the attribute
selection and training.  We found that in images with poor segmentations, the
confidences in prediction of car attributes were generally low.  One problem
with this implementation of attribute classifiers was that we didn't use
the selection criterion described in \cite{farhadi09} that enhances within
category prediction ability.  This means that, for example, the wheel attribute
is highly similar to the car attribute and thus its discrimative ability
is hurt.  One future direction for this research would be to improve the attribute
training using the additional selection criterion and observe effects on
the segmentations.

@@

The holy grail of this approach, of course, is to be able to segment objects
for which the canonical attribute distribution is unknown, based on a measure
of attribute coherence.  If this can be achieved, then segmentation experiments
could open up to non-experts, who could define coherence measures based on
semantic attributes and then could use this approach to automatically segment large
numbers of images even if no detection of their desired object exists.

Another problem with the attribute based method is that the attributes are not discriminative 
enough to separate different objects. For example, if we use the general attributes of head, torso and leg to 
do the object classification, we cannot separate dog and cat, since both of them have all of the attributes. 
But those attributes can definitely separate the two objects from non-animal objects, such as car. This example demonstrates that 
attributes are helpful for the object classification, but they are not discriminative enough. So one way to deal with this is to use 
both attributes features and low level objects features for object classification. We can train a general attributes models first. 
When we want to classify some specific objects, we can incorporate a small number of low level features from the specific object samples to the attributes 
features. In this way, we both reduce the training samples for object classification, and make the attribute based method more discriminative.

>>>>

\begin{table}
\centering
\begin{tabular}{|l|l|l|}
\hline Methods & Precision(\%) & Recall(\%) \\
\hline LowFea  & 55.97 & 70.96 \\
\hline Att1    & 51.89 & 51.89 \\
\hline Random  & 35.19 & 50.00 \\
\hline Add     & 60.82 & 54.06 \\
\hline
\end{tabular}
\caption{Object classification results of three baseline methods(LowFea, Att1 and Random) and the proposed additive algorithm(Add).}
\label{table:aresults}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/add_res/roc_class.png.eps}
\caption{ROC curves for object classification of car, aeroplane, horse and average.}
\label{fig:roc_class}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{figures/add_res/roc_seg.png.eps}
\caption{The curve of segmentation precision versus false positive classification rate.}
\label{fig:roc_seg}
\end{figure}

@@

\includegraphics[width=2.95cm]{figures/sub_results/2008_007064_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_000052_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_007171_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_000251_1_bad_sub.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars, which additive algorithm performs good.
  The first row shows the original image.  The second row shows
the segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm.}
\label{fig:car_good_results}
\end{figure*}

@@

\end{tabular}
\caption{Selected results from segmentation of cars, which subtractive algorithm performs good. 
 The first row shows the original image.  The second row shows
the segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm.}
\label{fig:car_bad_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg_2_good.jpg.eps} \\
\end{tabular}
\caption{Selected good results from segmentation of aeroplanes.  
The first row shows the original image.  The second row shows
the segmentation from the additive algorithm.}
\label{fig:aeroplane_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg_2_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg_2_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg_2_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg_2_bad.jpg.eps} \\
\end{tabular}
\caption{Selected bad results from segmentation of aeroplanes.
 The first row shows the original image.  The second row shows
the segmentation from the additive algorithm.}
\label{fig:aeroplane_bad_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg_3_good.jpg.eps} \\
\end{tabular}
\caption{Selected good results from segmentation of horses.  
The first row shows the original image.  The second row shows
the segmentation from the additive algorithm.}
\label{fig:horse_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg_3_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg_3_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg_3_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg_3_bad.jpg.eps} \\
\end{tabular}
\caption{Selected bad results from segmentation of horses.  
The first row shows the original image.  The second row shows
the segmentation from the additive algorithm.}
\label{fig:horse_bad_results}
\end{figure*}

@@

@@

As object classification is generally only as good as the features used, so also it
appears that this approach to segmentation is only as good as the attribute
selection and training.  We found that in images with poor segmentations, the
confidences in prediction of object-related attributes were generally low. Using bounding 
boxes as ground truth can introduce many background features into the attribute models. These 
features can be harmful. The extreme example is shown in the left image of figure \ref{fig:horse_bad_results}, 
which only segments out the background grass. However, even if we have the segmentation 
of objects as the ground truth for training the attributes, we may still not have accurate 
models, since the ground truth is for objects not for attributes. For example, if we train 
the attributes of wheel or metal only based on car images, we may get the car model not 
the attributes model. One way to deal with this problem is to directly label attributes 
ground truth. Then we can get similar accurate attribute models as the object models.

Another problem with the attribute based method is that the attributes are not discriminative 
enough to separate different objects. For example, if we use the general attributes of head, torso and leg to 
do the object classification, we cannot separate dog and cat, since both of them have all of the attributes. 
But those attributes can definitely separate the two objects from non-animal objects, such as car. So
attributes are helpful for object classification, but they are often not discriminative enough. One way to deal with this is to use 
both attributes features and low level objects features for object classification. We can train general attributes models first. 
When we want to classify some specific objects, we can incorporate a small number of low level features from the specific object samples to the attributes 
features. In this way, we both reduce the training samples for object classification, and make the attribute based method more discriminative.

Interestingly, the region pruning algorithms are feature-type independent.  That
is, they are not necessarily wedded to attribute features and could be used with
any feature type given a similarity scoring function.  Interesting future work would
be to try the pruning methods with lower-level features.

The holy grail of this approach, of course, is to be able to segment any object
with a given canonical attribute distribution.  If this can be achieved, 
then segmentation experiments
could open up to non-experts, who could define an attribute distribution
based on their own knowledge and use a system that has already been trained
on a large number of attributes to segment the object.
